---
title: "DV_FinalProject"
author: "Madeline Packard and Arthur DeVitalis"
date: "May 13, 2015"
output:
  html_document:
    theme: cerulean
    highlight: tango
---
For our final project, we wanted to explore data provided by the government of Canada through their Open Data portal. We choose this source for it's credibility, accessibility, and variety of datasets.


##The Data: College Graduates Survey

As college students, we were primarily interested in looking into Canadian college graduate data.
```{r, include=FALSE, results = "hide"}
source("../01 Data/packages.R", echo = FALSE)
```
```{r, message=FALSE}
source("../01 Data/Dataframes.R", echo = FALSE)
```

We pulled four datasets from a national survey of graduates data, which span over 2000, 2005, and 2010.

####Grad Earnings

```{r, eval=FALSE}
grad_earnings <- data.frame(fromJSON(getURL(URLencode(gsub("\n", " ", '129.152.144.84:5001/rest/native/?query= "select REF_DATE, GEO, SCHOOL, GENDER, STATS, VALUE from GRAD_EARNINGS "')),httpheader=c(DB='jdbc:oracle:thin:@129.152.144.84:1521:ORCL', USER='C##cs329e_map4542', PASS='orcl_map4542', MODE='native_mode', MODEL='model', returnDimensions = 'False', returnFor = 'JSON'), verbose = TRUE)))
```

```{r, message=FALSE, echo = FALSE}
tbl_df(grad_earnings)
```

####Grad Debt

```{r, eval=FALSE}
grad_debt <- data.frame(fromJSON(getURL(URLencode(gsub("\n", " ", '129.152.144.84:5001/rest/native/?query= "select REF_DATE, GEO, SCHOOL, SOURCE, STATS, VALUE from GRAD_DEBT "')),httpheader=c(DB='jdbc:oracle:thin:@129.152.144.84:1521:ORCL', USER='C##cs329e_map4542', PASS='orcl_map4542', MODE='native_mode', MODEL='model', returnDimensions = 'False', returnFor = 'JSON'), verbose = TRUE)))
```

```{r, message=FALSE, echo = FALSE}
tbl_df(grad_debt)
```

####Grad Employment

The Grad Employment dataset is nearly twice the size of our other datasets, and includes gender as a measure.

```{r, eval=FALSE}
grad_employment <- data.frame(fromJSON(getURL(URLencode(gsub("\n", " ", '129.152.144.84:5001/rest/native/?query= "select REF_DATE, GEO, SCHOOL, GENDER, STATS, VALUE from GRAD_EMPLOYMENT "')),httpheader=c(DB='jdbc:oracle:thin:@129.152.144.84:1521:ORCL', USER='C##cs329e_map4542', PASS='orcl_map4542', MODE='native_mode', MODEL='model', returnDimensions = 'False', returnFor = 'JSON'), verbose = TRUE)))
```

```{r, message=FALSE, echo = FALSE}
tbl_df(grad_employment)
```

####Grad Loans
```{r, eval=FALSE}
grad_loans <- data.frame(fromJSON(getURL(URLencode(gsub("\n", " ", '129.152.144.84:5001/rest/native/?query= "select REF_DATE, GEO, SCHOOL, SOURCE, STATS, VALUE from GRAD_LOANS "')),httpheader=c(DB='jdbc:oracle:thin:@129.152.144.84:1521:ORCL', USER='C##cs329e_map4542', PASS='orcl_map4542', MODE='native_mode', MODEL='model', returnDimensions = 'False', returnFor = 'JSON'), verbose = TRUE)))
```

```{r, message=FALSE, echo = FALSE}
tbl_df(grad_loans)
```